\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{classic} 
\moderncvcolor{blue}    

% Page margins
\usepackage[scale=0.88, top=1.2cm, bottom=1.2cm]{geometry}
\setlength{\hintscolumnwidth}{4.1cm} 

% Personal data
\name{Kristian Mark ``Shan''}{Surat}
\title{Full Stack Developer \& Graphic Designer}
\address{Marikina City, NCR}{Philippines}{}
\phone[mobile]{+63~969~832~8313}
\email{shansurat@pm.me}
\homepage{shansurat.dev}
\social[linkedin]{shansurat}
\social[github]{shansurat}

\begin{document}
\makecvtitle

\section{Professional Summary}
\cvitem{}{Results-driven Full Stack Developer and Graphic Designer with a 5-star freelance track record. Specializes in building \textbf{``secure by default''} web solutions, full-stack applications, and \textbf{automated data collection systems}. Expert in client management and cross-functional collaboration, bridging the gap between heavy backend coding and visual marketing needs. Proven reliability in end-to-end project execution.}

\section{Experience}
\cventry{Apr 2019 -- Present}{Freelance Web Developer \& Graphic Designer}{\href{https://www.freelancer.com/u/ksurat}{freelancer.com}}{Remote}{}{(Freelance) -- Maintained a 5-star rating with a 10\% repeat hire rate.{}%
\begin{itemize}%
    \item Developed responsive full-stack applications and custom WordPress environments, ensuring ``secure by default'' architecture.
    \item Bridged the gap between heavy backend development and marketing needs by handling end-to-end project lifecycles.
    \item Delivered high-quality work on time and within budget, resulting in consistent repeat business and referrals.
\end{itemize}}

\cventry{Feb 2026 -- Present}{3D Configurator Developer}{Blindspace AB}{Remote}{}{(Freelance) -- Specializing in interactive product visualization.{}%
\begin{itemize}%
    \item Engineered interactive 3D product configurators using DynaMaker, allowing for dynamic product visualization and customized user experiences.
    \item Integrated parametric 3D models seamlessly into the existing web platform to streamline digital product offerings.
\end{itemize}}

\cventry{Jun 2024 -- Present}{WordPress \& Full Stack Developer}{ScandiaPumps AB}{Remote}{}{(Full-time Jun 2024--Dec 2024; Part-time Jan 2025--Present){}%
\begin{itemize}%
    \item Engineered custom WordPress plugins and completely revamped a legacy business data dashboard, modernizing the UI and improving internal data visibility.
    \item Built and maintained full-stack applications, integrating advanced features such as text-to-speech capabilities to enhance project functionality.
\end{itemize}}

\cventry{Apr 2023 -- May 2024}{Full Stack Web Developer}{infinityprojectors.com}{Remote}{}{(Full-time){}%
\begin{itemize}%
    \item Managed end-to-end e-commerce development, significantly improving overall UI/UX by redesigning high-converting product pages.
    \item Designed custom product imagery and graphic assets, seamlessly integrating visual marketing materials with customized front-end web solutions.
\end{itemize}}

\cventry{Jun 2023 -- Aug 2023}{Web Developer \& Library Intern}{CSWCD Library, UPD}{Quezon City}{}{(Internship / Part-time){}%
\begin{itemize}%
    \item Developed and maintained the library's website to ensure functionality, accessibility, and user-friendliness for researchers.
    \item Automated organizational records management and updated library materials to ensure catalog accuracy.
\end{itemize}}

\cventry{Apr 2022 -- Apr 2023}{Programmer \& UX Designer}{Marfox}{UK (Remote)}{}{(Full-time){}%
\begin{itemize}%
    \item Developed and maintained the company's web applications using modern JavaScript frameworks to improve performance and scalability.
    \item Designed intuitive and visually appealing user interfaces based on user research and feedback.
    \item Created wireframes, mockups, and prototypes to visualize and test design concepts prior to implementation.
\end{itemize}}

\section{Selected Projects}
\cvitem{samoayoub.com}{Orchestrated the migration of a high-fidelity Webflow design to a custom WordPress environment, implementing complex GSAP animations for a premium, interactive user experience.}
\cvitem{natureofficial.com}{Designed and developed a bespoke WordPress platform for a professional music artist, focusing on high-performance multimedia integration and brand-consistent aesthetics.}
\cvitem{3D Product Configurator}{Architected a parametric 3D visualization tool using DynaMaker for Blindspace AB, reducing the sales cycle by providing instant visual quotes to customers.}
\cvitem{Business Intelligence Dashboard}{Rebuilt a legacy PHP/SQL dashboard for ScandiaPumps AB, implementing modern data visualization, \textbf{Python-driven data processing}, and secure authentication protocols.}

\section{Technical \& Design Skills}
\cvitem{Full Stack}{Next.js, React, Vue.js, Angular, Laravel, PHP, Python, JavaScript (ES6+), GSAP Animations}
\cvitem{CMS \& E-Comm}{WordPress (Custom Plugin \& Theme Dev), WooCommerce, Webflow-to-WP Migration}
\cvitem{Backend \& Data}{Python (Scrapy, Selenium, BeautifulSoup), MySQL, PostgreSQL, Firebase, Neo4j, CouchDB, Data Scraping, Information \& Data Management (LIS)}
\cvitem{Design \& UI/UX}{Professional Graphic Design, Figma, DynaMaker (3D Configurators), Wireframing, Mockups}
\cvitem{Competencies}{Technical Documentation, Agile Workflow, Remote Collaboration, Client Relationship Management}

\section{Languages}
\cvitemwithcomment{English}{Professional Working Proficiency}{}
\cvitemwithcomment{Filipino}{Native Proficiency}{}

\section{Education}
\cventry{2027}{Bachelor of Library and Information Science}{University of the Philippines Diliman (UPD)}{Quezon City}{}{Focus on Information Organization, Records Management, and Systems Technology.}

\section{Leadership \& Extracurricular}
\cventry{Aug 2023 -- May 2024 \newline Jul 2020 -- Jul 2021}{Executive Secretary}{UP FLIPP}{Quezon City}{}{Led the Records and Documentation Committee.{}%
\begin{itemize}%
    \item Implemented efficient systems for managing and archiving organizational records, significantly improving information retrieval.
    \item Documented events and activities, creating comprehensive reports for future reference.
\end{itemize}}

\end{document}